---
output: html_document
resource_files:
- allData.rdata
- selTab.csv
- boxplots.r
- plots.r
- violins.r
runtime: shiny
---
```{r echo=FALSE,message=FALSE,warning=FALSE}
library(knitr)
library(lubridate);library(shiny)
library(data.table)
library(ggplot2)
library(dplyr)
library(curl)

load("allData.rdata")
allData$dSM <- NA
selTab <- fread("selTab.csv")
read_chunk('plots.r')
read_chunk('violins.r')
read_chunk('boxplots.r')
```

---
title: "VdL Documentation"
author: "Walt Ludwick"
date: "December 11, 2018"
output: html_document
runtime: shiny
---


This R Markdown document is made interactive using Shiny. Unlike the more traditional workflow of creating static reports, you can now create documents that allow your readers to change the assumptions underlying your analysis and see the results immediately. To learn more, see [Interactive Documents](http://rmarkdown.rstudio.com/authoring_shiny.html).

## Inputs and Outputs

You can embed Shiny inputs and outputs in your document. Outputs are automatically updated whenever inputs change.  This demonstrates how a standard R plot can be made interactive by wrapping it in the Shiny `renderPlot` function. The `selectInput` and `sliderInput` functions create the input widgets used to drive the plot.


## Embedded Application: Line graph plot

It's also possible to embed an entire Shiny application within an R Markdown document using the `shinyAppDir` function. This example embeds a Shiny application located in another directory.  It enables us to plot data from soil sensors, according to parameters set by the user, for:

* X and Y axes: Can set your choice of parameters measured by the soil sensor (including date/time stamp of readings)
* Timestep (set increment) and Start/End dates (set the range)
* Classification: Filter by functional class(es) and/or zone class(es) you'd like to see displayed.


# creates plots
```{r first,echo=FALSE,message=FALSE,warning=FALSE}
<<plots>>
```


## Embedded Application:  Violin Plots
Allows you to view distribution of data selected -much like the boxplot (see below), only with the added nuance of kernel density.

# creates violin plots
```{r second,echo=FALSE,message=FALSE,warning=FALSE}
<<violin>>
```


## Embedded Application: Box Plots

The classic view of data distribution, divided into quartiles.  The line in middle of boxplot represents medium, and the "whisker" lines at top and bottom extend to max and min values, respectively.

# create boxplots
```{r third,echo=FALSE,message=FALSE,warning=FALSE}
<<boxplots>>
```

