---
output: html_document
resource_files:
- allData.rdata
- selTab.csv
- boxplots.r
- plots.r
- violins.r
runtime: shiny
---
```{r echo=FALSE,message=FALSE,warning=FALSE}
library(knitr)
library(lubridate);library(shiny)
library(data.table)
library(ggplot2)
library(dplyr)
library(curl)

load("allData.rdata")
allData$dSM <- NA
selTab <- fread("selTab.csv")
read_chunk('plots.r')
read_chunk('violins.r')
read_chunk('boxplots.r')
```

---
title: "vdl documentation"
author: "francesco minunno"
date: "December 11, 2018"
output: html_document
runtime: shiny
---


This R Markdown document is made interactive using Shiny. Unlike the more traditional workflow of creating static reports, you can now create documents that allow your readers to change the assumptions underlying your analysis and see the results immediately. 

To learn more, see [Interactive Documents](http://rmarkdown.rstudio.com/authoring_shiny.html).

## Inputs and Outputs

You can embed Shiny inputs and outputs in your document. Outputs are automatically updated whenever inputs change.  This demonstrates how a standard R plot can be made interactive by wrapping it in the Shiny `renderPlot` function. The `selectInput` and `sliderInput` functions create the input widgets used to drive the plot.


## Embedded Application

It's also possible to embed an entire Shiny application within an R Markdown document using the `shinyAppDir` function. This example embeds a Shiny application located in another directory:


# creates plots
```{r first,echo=FALSE,message=FALSE,warning=FALSE}
<<plots>>
```


## Embedded Application
write something here to describe violins plots

# creates violin plots
```{r second,echo=FALSE,message=FALSE,warning=FALSE}
<<violin>>
```


## Embedded Application

write something here to describe boxplots

# create boxplots
```{r third,echo=FALSE,message=FALSE,warning=FALSE}
<<boxplots>>
```

